Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

	 Another example for the GA pseudo-hardness function family?
		sqaure and sqrt.

	 Loss normalization with $u$?

>>>>

\noindent\textbf{I. Parameters or Adjustable Items}

The parameters, namely $u$ and $\xi$ are discussed in the previous section
of this supplementary material, see ``Performance-Sensitive Factors''.

~\newline
\noindent\textbf{II. Non-linear Graduate Adversary}

In the manuscript, Linear Graduate Adversarial is demonstrated effective,
and more complicated choices are left for future work.
%
Here we provide two Non-linear Graduate Adversary examples, namely
$g_\mathsf{2}$ and $g_\mathsf{1/2}$, as follows:
%
\begin{align}
	g_\mathsf{2}(\cdot)   &= -\gamma \cdot (\bar{\ell}_{t-1})^{2}  &~ \in [-\gamma,0]\\
	g_\mathsf{1/2}(\cdot) &= -\gamma \cdot (\bar{\ell}_{t-1})^{1/2} &~ \in [-\gamma, 0]
\end{align}
%
Compared to LGA, $g_\mathsf{2}$ is more ``eager'' to result in strong adversarial
examples in the early phase of training, while $g_\mathsf{1/2}$ is more ``conservative''
in creating strong adversarial examples in the early phase of training
(adversarial examples from HM are stronger if the function value is closer to $0$).
